\documentclass[12pt, titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{array}
\usepackage{longtable}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm]{geometry}

\title{Weather App User Manual}

\author{Kyle Chestnut, Caleb Newman, Trey Coleman, Alan Huebschen}

\begin{document}

\maketitle

\section*{Installation}

Simply download the executable file and place the file in your desired location, the only requirement is that you be running the x64 version of Windows 10. The executable can be run as-is. 300MB of storage required.

\section*{Usage}

To start the forecast app, you will need to double click WeatherApp.exe. Something to note: there is a significant startup time when starting the application. The app will allow you to search the 5-day forecast of a location. The program will detect the user’s current location based on their external IP address. When the program is first ran, the program will display the weather based on the estimated location of the user’s IP. If the user would like to view the weather at a different location, they may enter the name of a city or a zip code in the text input box and click the “Get Weather” button at the bottom. Using the zip code of the desired location is recommended to ensure finding the correct location.


\section{Bugs and test cases}

\begin{longtable}{>{\hspace{0pt}}m{0.048\linewidth}>{\hspace{0pt}}m{0.253\linewidth}>{\hspace{0pt}}m{0.196\linewidth}>{\hspace{0pt}}m{0.382\linewidth}>{\hspace{0pt}}m{0.044\linewidth}}
Test Case \# & Input & Expected Output & Rationale & Pass/ Fail \endfirsthead 
\hline
1 & Put in Very long text into prompt.~ Ex.~ Copy and paste hamlet & Catches the long output without crashing.~ Returns no town found. & We should limit the user to only input what is necessary for cities. & Pass \\
2 & Check for cursor blink throughout tests. & No output for this. & The user interface should not appear buggy. & Pass \\
3 & Drag and drop long text & Catches the long output without crashing.~ Returns no town found. & While copy and paste is allowed for longer city names.~ We should make sure that the input is valid. & Pass \\
4 & Check with different language options & Works normally, returning nothing if not recognized, or returning weather of location if accounted for by API & If users do not primarily use the english language we should account for whatever language they speak and write in. & Pass \\
5 & Hold down a single key for an extended period & Returns no town found. & We should only allow valid cities. & Pass \\
6 & Try to input an image in multiple fashions (different file types, drag and drop, copy and paste.) & Returns no town.~ Might just reject the input. & The text box should only allow for text input. & Pass \\
7 & Test for null/ blank & Does not search, or no town found. & Users may accidentally delete their city entry before getting their forecast & Pass \\
8 & Max character test & Catches that there are more characters than the box allows, or caps the amount of characters when put into the box. & There should not be a way for the user to “overflow” our program or the API we are using so a max length on the text box will be added & Pass \\
9 & Symbols of varying origin (Alt key symbols, characters from different alphabets, numbers, symbols, numbers, etc.) & Works normally, or returns default value. & Some cities may contain letters not a part of the English alphabet.~ As long as the city name is valid the city should be returned. & Pass \\
10 & Ascii characters. & Ascii is not supported and therefore should return an error. & The user should only be able to enter valid text. & Pass \\
11 & Control characters & Control characters are not supported and therefore should return an error & The user should only be able to enter valid text. & Pass \\
12 & Boundary values test & If the city is valid and is within the boundaries that have been set then we return the city.~ If not we return an error & The boundary values that were set for the text box should not be violated. & Pass \\
13 & Are the characters properly visible in text input? & Normal output.~ Should be able to see text input. & The user should clearly see what city they are attempting to input. & Pass \\
14 & Basic city name test & Returns the town name and weather~ & The user should be able to enter a town name and get the weather for that town. & Pass \\
15 & Basic zip code test & Returns the town name and weather based on the zip code provided. & The user should be able to enter a zip code and get the weather for that location. & Pass \\
16 & Check for pasting unusual characters in the text field. & Should not crash or glitch. & With unusual input the program itself should not crash and just return an error that a city cannot be found. & Pass \\
17 & Enter spaces in the prefix and suffix of what you type. & The program handles spaces before and after the town name, and return proper weather results & As long as the name of the town is valid, it should return the results. & Pass \\
18 & Does any elements of the program change position through repeated use of the program? & No output.~ Just watch. & The user should be able to input as many locations as they want in a singular run of the program.~ Although it will be done one at a time, the location of each component should be static and the information should not deviate from its original position. & Pass \\
19 & Check if repeatedly pressing the forecast button many times crashes the program or glitches it out.~ (do this with both an empty field and non empty field) & The program will function every time without crashing. & If the user is clicking the “Get Forecast” button repeatedly the program should function no differently. & Pass \\
20 & Check for only spaces as input. & Returns no city found because spaces are not a valid input for a city. & We want to account for most if not all cases of user input. & Pass \\
21 & Does copying from the text box work? & No crash or error. & A user should be able to copy and paste into the text box. & Pass \\
22 & Enter a mix of numbers and characters into the text box. & Return no city found & A user should be allowed to enter a city or zip code but not a combination of the two. & Pass \\
23 & Enter a city name with a space in the middle of the name. Example: Spring field & Return no city found & A user may accidentally space in the middle of a city name without noticing.~ We want to be able to catch that error & Pass \\
24 & Enter a city name with a space in the middle of a name.~\par{}Example: San Jose & Return the proper city and weather. & A user may enter a city that specifically has a space in between two words.~~ & Pass \\
25 & VPN and proxy & Should return the weather based on the default I.P. & Users may have an active VPN or proxy server on their machine. & Fail
\end{longtable}

\end{document}
